A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-08 paper/elsarticle/elsarticle-template.tex
paper

We propose a spatial AR system that produces the effect of keystone correction analytically, and that facilitates placement by intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downward toward the scene plane. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling wide-area factory floor augmentation exceeding the bounds of the projector's own immediate field of view.
\end{abstract}

@@

\begin{figure}
    \centerline{\includegraphics[scale=.35]{images/2d3d.png}}
    \caption{Scene plane (gray) obtained via spatial resection with respect to 2D-3D correspondences obtained using a chessboard pattern (blue); 3D circles pattern points obtained by intersection with the scene plane of back-projections (likewise gray) of circles pattern center points detected in the image plane (red). Note that the points in the figure are the points recovered for the projector calibration image in Figure~\ref{fig:2d}(b), acquired by the camera (frustum in black, with up vector in red).}
    \label{fig:3d}
\end{figure}

@@

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); next, we (ii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Separately, we (iii) carry out steps (i) and (ii) for the downward-facing camera, giving a virtual camera likewise facing directly\footnote{A physical camera placed to face downwards is likely to not face downwards precisely; in contrast, the virtual camera's optical axis is aligned exactly with the scene plane's normal vector, rendering it fronto-parallel with respect to the scene plane.} downwards to the scene plane. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector. The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions.

@@

\paragraph{Plane-induced homography} Let $\mathtt{K}_\text{proj}$ express the calibration matrix of the recovered projector and $(\mathtt{R}, \mathbf{t}) \in SE(3)$ the rigid body transformation that transforms points from the coordinate frame of the recovered projector to that of the virtual projector, for a given target location. Moreover, let $(\mathbf{n}^\top, -d)^\top$ give the scene plane, expressed in the coordinate frame of the recovered projector, where $\mathbf{n} \in \mathbb{R}^3$ is the scene plane's normal vector and $d = \mathbf{n}^\top\mathbf{X}$, for any point $\mathbf{X}$ in the plane. The transformation that distorts the image to be projected to the scene plane by the recovered projector such that it appear as if were projected to the scene plane by the virtual projector is given the by the $3~\times~3$ matrix
\begin{equation}
\mathtt{H} = \mathtt{K}_\text{proj}\left(\mathtt{R} - \frac{\mathbf{t}\mathbf{n}^\top}{d}\right)\mathtt{K}_\text{proj}^{-1},
\label{homgen}
\end{equation}
a form of `plane-induced' homography \cite{Hartley2004}. For convenience, we enable optional scaling or rotation of the image to be projected \textit{before} applying the homography; that rotation, parameterized in degrees, is thus in effect carried out intuitively relative to the placement of the camera.

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik using our approach and two variants of a baseline approach (`Baseline A' and `Baseline B'). At each of the 15 locations, we aim to augment the scene by placing an image aligned with the principal axes of the floorspace and such that the image appear in each instance to be free of projective distortions and to have the same dimensions (30 cm $\times{}$ 20 cm). Using our approach to carry out keystone correction automatically, we carried out all steps---which we further detail in Figure X---within a time budget of 15 min. Accordingly, we set 15 min to be the time budget of the first variant of the baseline approach (`Baseline A'), in which we carry out a \texit{manual} keystone correction using the software bundled with the steerable mirror system mounted alongside our projector. We then compare the quality of the augmentations produced with this baseline with those produced using our approach. The second variant of the baseline approach (`Baseline B') is to again use the bundled software to carry out keystone correction manually, but to record how much time is necessary to produce augmentations within a mean tolerance of 1 cm. The steps for the baseline approaches are detailed in Figure Y. All experiments were carried out jointly by the same experienced technician and assistant.

The hardware setup employed in the evaluation comprised a Panasonic PT-RZ660BE projector with a steerable mirror system manufactured by Dynamic Projection Institute \cite{rupprecht2020information}. In addition, we used a Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The setup was mounted on the ceiling of the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. The floorspace used for our experiments measured dimensions of ca.\ X~m~$\times$~Y~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.

\paragraph{Our approach} ...

>>>>

We propose a spatial AR system that produces the effect of keystone correction analytically, and that facilitates placement by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downward toward the scene plane. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling wide-area factory floor augmentation exceeding the bounds of the projector's own immediate field of view.
\end{abstract}

@@

\begin{figure}
    \centerline{\includegraphics[scale=.35]{images/2d3d.png}}
    \caption{Scene plane (gray) obtained via spatial resection with respect to 2D-3D correspondences obtained using a chessboard pattern (blue); 3D circles pattern points obtained by intersection with the scene plane of back-projections (likewise gray) of circles pattern center points detected in the image plane (red). Note that the points in the figure are the points recovered for the projector calibration image in Figure~\ref{fig:2d}(b), acquired by the camera (frustum of the camera in black, with up vector in red).}
    \label{fig:3d}
\end{figure}

@@

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); next, we (ii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Separately, we (iii) rotate the camera about its center of projection to align its optical axis with the normal vector of the scene plane, giving a virtual camera likewise facing directly\footnote{A physical camera placed to face downwards is likely to not face downwards precisely; in contrast, the virtual camera's optical axis is aligned exactly with the scene plane's normal vector, rendering it fronto-parallel with respect to the scene plane.} downwards to the scene plane. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector. The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions. Optionally, we additionally adjust the height above the scene plane of the virtual projector, in order to satisfy desired projected image dimensions provided in metric units.

@@

\paragraph{Plane-induced homography} Let $\mathtt{K}_\text{proj}$ express the calibration matrix of the recovered projector and $(\mathtt{R}, \mathbf{t}) \in SE(3)$ the rigid body transformation that transforms points from the coordinate frame of the recovered projector to that of the virtual projector, for a given target location. Moreover, let $(\mathbf{n}^\top, -d)^\top$ give the scene plane, expressed in the coordinate frame of the recovered projector, where $\mathbf{n} \in \mathbb{R}^3$ is the scene plane's normal vector and $d = \mathbf{n}^\top\mathbf{X}$ for any point~$\mathbf{X}$ in the plane, so that $(\mathbf{n}^\top, -d) (\mathbf{X}^\top, 1)^\top = 0$. The transformation that distorts the image to be projected to the scene plane by the recovered projector such that it appear as if were projected to the scene plane by the virtual projector is given the by the $3~\times~3$ matrix
\begin{equation}
\mathtt{H} = \mathtt{K}_\text{proj}\left(\mathtt{R} - \frac{\mathbf{t}\mathbf{n}^\top}{d}\right)\mathtt{K}_\text{proj}^{-1},
\label{homgen}
\end{equation}
a form of `plane-induced' homography \cite{Hartley2004}. For convenience, we enable optional rotation of the image to be projected \textit{before} applying the homography; that rotation, parameterized in degrees, is thus in effect likewise carried out intuitively relative to the placement of the camera.

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with two variants of a baseline approach involving manual keystone correction (`Baseline A' and `Baseline B'), by aiming to place an image for each location aligned with the principal axes of the floorspace, absent projective distortions, and with the same dimensions (30 cm $\times{}$ 20 cm). Using our approach to carry out keystone correction analytically, we carried out all steps within a time budget of 15 min. Accordingly, we set 15 min to be the time budget of the first variant of the baseline approach (`Baseline A'), in which we carry out a \texit{manual} keystone correction using the software bundled with the steerable mirror system mounted alongside our projector. The second variant of the baseline approach (`Baseline B') is to again use the bundled software to carry out keystone correction manually, but to record how much time is necessary to produce augmentations within a mean tolerance of XX. All experiments were carried out jointly by the same experienced technician and assistant.

The hardware setup employed in the evaluation comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information}, bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downward-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The setup was mounted on the ceiling of the Pilotfabrik. The floorspace used for our experiments measured dimensions of ca.\ X~m~$\times$~Y~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.

\paragraph{Our approach} We begin by carrying out a one-time\footnote{Note that once the camera is calibrated, that calibration can be reused if the camera's pose relative to the projector-steerable mirror system remains fixed.} calibration of the camera, acquiring 10 camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) and feeding the images as input to our camera calibration module. Separately, for each of the 15 target locations, we produce a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting the circles pattern image to the location in question using the steerable mirror, placing a checkerboard pattern beside the projected pattern, and acquire the image using the downward-facing camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the steerable mirror is made to point to that location, the circles pattern image is projected to the scene plane, an image is acquired using the camera, and the location is registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warp the images to be projected to the respective locations using their corresponding homography, using a third dedicated module. These warped images are finally imported into the MDC-X software and associated with their respective location presets.

The total amount of time to carry out all the above steps amounted to ca.\ 15 min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 4 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software.
